---
title: "Cannabis Control"
author: "Ikemonso"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Often times, the average smokers claim that "it doesn't matter as long as I get high" while more seasoned users understand that characteristics such as strain, aroma, and taste, can be important factors in the day-to-day smoke sessions. In this project we'll look at those different factors and try to isolate the difference in the strains provided by the dataset

## Libraries & Packages
```{r}
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(mdsr)
library(janitor)
library(stringr)
library(stringi)
library(ggfittext)
library(ISOweek)
cannabis <- read_csv("/Users/ikospiko/Desktop/DATA_PROJECTS/Nintendo_DS/Cannabis Analysis Project/Cannabis_Project/Data/cannabis.csv")
```


## Worst Weed
### Let's look at the strain that's done the worst and see if we can find any trends that may dampen user experience.
```{r}
worst <- cannabis %>% 
  arrange(Rating) %>% 
  head(10) %>% 
  select(Strain, Type, Effects, Flavor)
worst

#Now that we've seen the bottom 10, we'll see what characteristic (type, flavor, or effect) is most likely to effect rating
#First we compare the effects with the Effects column, a quick look at the table again shows us that we have many "None" values so we'll use this as the true statement to get the proportion


worst_type <- worst %>% 
  count(Type) %>% 
  mutate(TypeProportion = prop.table(n))


```


## Trust the process
### At some point, every experienced smoker has thought about growing their own plant. But the benefits of a personal source are outweighed by the responsbility it requires (especially in terms of time). Let's see if we can isolate the strain that's easiest to produce, time-wise.
```{r}
#duration <- cannabis %>% 
#Filter Descriptions that include growth cycle duration  
#  filter(str_detect(Description, "\\d+\\s*(day|week|month|year)"),
 #        str_detect(Description, "[0-9]+[- ][a-zA-Z]+")) %>% 
  #arrange(Rating) %>% 
  #head(5) %>% 
  #pull(Description)
#duration

```
